Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"

### 2023-01-13 MCK-manuscript/Supplementary/MCK-supplementary.tex
fixed punctuation and equation in main ans supp

\documentclass[12pt]{iopart}
\usepackage{iopams}  
\usepackage{braket,graphicx,amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=2cm]{geometry}
\bibliographystyle{unsrt}
\begin{document}

@@

\subsection{Partition function of the zero-mode fixed-point Hamiltonian, in the presence of a magnetic field}
The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
\begin{eqnarray}
	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
\end{eqnarray}
where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels. We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
\begin{eqnarray}
	\label{stargraph_field_hamiltonian}
	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
\end{eqnarray}
The Hamiltonian commutes with \(s_\text{tot}^2\):
\begin{eqnarray}
	\hspace*{-20pt}\left[s_\text{tot}^2, H(h)\right] &= \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\}\nonumber\\
							 &= 0
\end{eqnarray}
This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\). Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\). For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \). The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\). From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\). So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\). We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on where it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks. To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)). The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \). The fact that this block does not interact with the other blocks can be observation: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down. This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.

Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{eqnarray}
	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
\end{eqnarray}
The eigenvalues are 
\begin{eqnarray}
	\label{eigenvalue}
	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
\end{eqnarray}
where \(\alpha = \epsilon^h_m + J/4\).
The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}. This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
The eigenstates for each value of \(M,m\) in the \(J=M-\frac{1}{2}\) sector are given by
\begin{eqnarray}
	\fl \ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, ~ ~ \mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}
\end{eqnarray}
The partition function is given by
\begin{eqnarray}
	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{eqnarray}
where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\). This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\). For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\). \(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\). So, \(s_\text{tot} = 1/2\) appears twice. These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different. We need to count the number of instances of a particular subspace \(s_\text{tot}=M\). It turns out that this number is given by \(r^K_M = {}^{K-1}C_{K/2 - M}\), which means the correct partition function is
\begin{eqnarray}
	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{eqnarray}

\subsection{Features of the polarised ground-states}
Of particular importance within the ground-state subspace are the zero-field maximally-polarised states, obtained by choosing \(M = \frac{K}{2}, m + \frac{1}{2}= \pm \left( M - \frac{1}{2} \right) =\pm \frac{1}{2}\left(K-1\right)\):
\begin{eqnarray}
	\fl \ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
\end{eqnarray}
where \(\sigma\) can take values \(\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin. The state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\) has all the bath spins pointing in the \(\sigma-\)direction: \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}} = \ket{\sigma,\sigma,\ldots,\sigma} (\sigma=\uparrow \text{ or }\downarrow)\), where the notation is such that a particular symbol (say \(\uparrow\)) at the \(i^\text{th}\) position indicates the configuration of the \(i^\text{th}\) channel. The other state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)}\) can be obtained by flipping any one out of the \(K\) spins in the previous state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\), leading to the normalised state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)} = \frac{1}{\sqrt K}\ket{\bar\sigma,\sigma,\ldots,\sigma} + \frac{1}{\sqrt K}\ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \frac{1}{\sqrt K}\ket{\sigma,\sigma\ldots,\bar\sigma}\), a linear combination of all possible states with the spin of one channel in \(\bar\sigma(=-\sigma)\) direction and all other channels remaining in the \(\sigma\) direction. With these in mind, the polarised state can be cast in the more explicit form
\begin{eqnarray}
	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) - K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}\qquad
\end{eqnarray}

In order to make the frustration faced by the impurity manifest, we now rewrite these polarised states in the form of superpositions of zero magnetisation singlet states. Let us define the singlet state \(\ket{\text{SS}_{d,l}} = \frac{1}{\sqrt 2}\left(\ket{\uparrow}_d\ket{\downarrow}_l - \ket{\downarrow}_d\ket{\uparrow}_l\right),l\in[1,K]\), between the impurity spin and the \(l^\text{th}\) channel, where \(\ket{\cdot}_l\) represents the configuration of the spin in the \(l^\text{th}\) channel. The polarised states can then be written as
\begin{eqnarray}
	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime} = \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
\end{eqnarray}
This form of the state shows that the impurity is trying to participate, simultaneously, in forming \(K\) number of singlets. Put differently, the presence of \(K\) singlets shows that all \(K\) channels are trying to screen the impurity simultaneously. However, the presence of an overall non-zero magnetisation in the states means that the screening is only partial.

From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations. For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\ref{polarised-state} involve the impurity hybridising with the bath. In eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel. Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\). The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in Eq.~\ref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels. This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel. With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
\begin{eqnarray}
	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
\end{eqnarray}
This result then connects to the Friedel scattering phase shift (eq.(20) of the main manuscript) and the magnetisation of the impurity (eq.(21) of the main manuscript). In this way, the excess charge $n_\text{exc}^{(l)}$ of the star graph is also observed to guide the RG flow of the MCK problem to the intermediate coupling fixed point (eq.(55) of the main manuscript), and lead to the power-law behaviour of various thermodynamic quantities at the fixed point (eq.(56) of the main manuscript).

\subsection{Energy lowering due to quantum fluctuations}
The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
\begin{eqnarray}
	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
	\label{eq:stargraph_hamiltonian}
\end{eqnarray}
We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state. This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\). In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
\begin{eqnarray}
	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, \quad E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
\end{eqnarray}  
where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text. This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph. Note that because of the degeneracy of the ground state subspace, there are multiple ground states characterised by different values of \(J^z = S^z + S_d^z\), and different ground states lead to different values of \(E_Q\).

The variation of \(E_Q\) is shown in Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated. For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$). The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem. This behaviour persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit. On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.

@@

Calculating the staggered magnetization for a general multichannel problem with \(K\) channels and a spin-\(S_d\) impurity reveals the breakdown of screening brought about by the presence of multiple channels. We find, in general, that the square of the staggered magnetization per channel is
\begin{eqnarray}
	\fl m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
\end{eqnarray}

@@

	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}

@@

	\implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}

>>>>

\documentclass{iopart}
\usepackage{iopams}  
\usepackage{braket,graphicx,cite,amsmath}
\usepackage[colorlinks,linkcolor={blue},citecolor={blue}]{hyperref}
\usepackage[margin=2cm]{geometry}
\bibliographystyle{unsrt}
\begin{document}

@@

\subsection{Partition function of the zero-mode fixed-point Hamiltonian, in the presence of a magnetic field}
The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
\begin{eqnarray}
	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}~,
\end{eqnarray}
where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels. We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
\begin{eqnarray}
	\label{stargraph_field_hamiltonian}
	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z~.
\end{eqnarray}
The Hamiltonian commutes with \(s_\text{tot}^2\):
\begin{eqnarray}
	\left[s_\text{tot}^2, H(h)\right] &= \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\}\nonumber\\
							 & = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0~.
\end{eqnarray}
This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\). Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\). For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \). The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\). From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\). So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\). We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on where it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks. To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)). The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \). The fact that this block does not interact with the other blocks can be observation: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down. This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.

Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{eqnarray}
	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} ~.
\end{eqnarray}
The eigenvalues are 
\begin{eqnarray}
	\label{eigenvalue}
	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}~,
\end{eqnarray}
where \(\alpha = \epsilon^h_m + J/4\).
The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\eqref{eigenvalue}. This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
The eigenstates for each value of \(M,m\) in the \(J=M-\frac{1}{2}\) sector are given by
\begin{eqnarray}
	\ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, \\
	\mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}~.
\end{eqnarray}
The partition function is given by
\begin{eqnarray}
	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]~,
\end{eqnarray}
where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\). This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\). For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\). \(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\). So, \(s_\text{tot} = 1/2\) appears twice. These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different. We need to count the number of instances of a particular subspace \(s_\text{tot}=M\). It turns out that this number is given by \(r^K_M = {}^{K-1}C_{K/2 - M}\), which means the correct partition function is
\begin{eqnarray}
	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]~.
\end{eqnarray}

\subsection{Features of the polarised ground-states}
Of particular importance within the ground-state subspace are the zero-field maximally-polarised states, obtained by choosing \(M = \frac{K}{2}, m + \frac{1}{2}= \pm \left( M - \frac{1}{2} \right) =\pm \frac{1}{2}\left(K-1\right)\):
\begin{eqnarray}
	\ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} \nonumber\\
	= \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
\end{eqnarray}
where \(\sigma\) can take values \(\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin. The state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\) has all the bath spins pointing in the \(\sigma-\)direction: \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}} = \ket{\sigma,\sigma,\ldots,\sigma} (\sigma=\uparrow \text{ or }\downarrow)\), where the notation is such that a particular symbol (say \(\uparrow\)) at the \(i^\text{th}\) position indicates the configuration of the \(i^\text{th}\) channel. The other state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)}\) can be obtained by flipping any one out of the \(K\) spins in the previous state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\), leading to the normalised state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)} = \frac{1}{\sqrt K}\ket{\bar\sigma,\sigma,\ldots,\sigma} + \frac{1}{\sqrt K}\ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \frac{1}{\sqrt K}\ket{\sigma,\sigma\ldots,\bar\sigma}\), a linear combination of all possible states with the spin of one channel in \(\bar\sigma(=-\sigma)\) direction and all other channels remaining in the \(\sigma\) direction. With these in mind, the polarised state can be cast in the more explicit form
\begin{eqnarray}
	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} &\left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) \right.\nonumber\\
										&\left.- K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}\qquad
\end{eqnarray}

In order to make the frustration faced by the impurity manifest, we now rewrite these polarised states in the form of superpositions of zero magnetisation singlet states. Let us define the singlet state \(\ket{\text{SS}_{d,l}} = \frac{1}{\sqrt 2}\left(\ket{\uparrow}_d\ket{\downarrow}_l - \ket{\downarrow}_d\ket{\uparrow}_l\right),l\in[1,K]\), between the impurity spin and the \(l^\text{th}\) channel, where \(\ket{\cdot}_l\) represents the configuration of the spin in the \(l^\text{th}\) channel. The polarised states can then be written as
\begin{eqnarray}
	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} &= \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\nonumber \\
						    &= \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
\end{eqnarray}
This form of the state shows that the impurity is trying to participate, simultaneously, in forming \(K\) number of singlets. Put differently, the presence of \(K\) singlets shows that all \(K\) channels are trying to screen the impurity simultaneously. However, the presence of an overall non-zero magnetisation in the states means that the screening is only partial.

From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations. For this, we first note that the form eq.~\eqref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\eqref{polarised-state} involve the impurity hybridising with the bath. In eq.~\eqref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel. Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\). The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in eq.~\eqref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels. This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel. With these in mind, the total excess charge contributed to each channel from the state in eq.~\eqref{polarised-state} is
\begin{eqnarray}
	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}~.
\end{eqnarray}
This result then connects to the Friedel scattering phase shift (eq.(20) of the main manuscript) and the magnetisation of the impurity (eq.(21) of the main manuscript). In this way, the excess charge $n_\text{exc}^{(l)}$ of the star graph is also observed to guide the RG flow of the MCK problem to the intermediate coupling fixed point (eq.(55) of the main manuscript), and lead to the power-law behaviour of various thermodynamic quantities at the fixed point (eq.(56) of the main manuscript).

\subsection{Energy lowering due to quantum fluctuations}
The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
\begin{eqnarray}
	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
	\label{eq:stargraph_hamiltonian}
\end{eqnarray}
We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\eqref{eq:stargraph_hamiltonian} stabilises the ground state. This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\). In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
\begin{eqnarray}
	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, \quad E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
\end{eqnarray}  
where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text. This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph. Note that because of the degeneracy of the ground state subspace, there are multiple ground states characterised by different values of \(J^z = S^z + S_d^z\), and different ground states lead to different values of \(E_Q\).

The variation of \(E_Q\) is shown in Fig.\eqref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated. For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$). The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem. This behaviour persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit. On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.

@@

Calculating the staggered magnetization for a general multichannel problem with \(K\) channels and a spin-\(S_d\) impurity reveals the breakdown of screening brought about by the presence of multiple channels. We find, in general, that the square of the staggered magnetization per channel is
\begin{eqnarray}
	m_s^2 &= \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
	      &= \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
\end{eqnarray}

@@

	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}~.

@@

	\implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}~.
